MIP-GNN: A data-driven tool for guiding combinatorial solvers

### 2020-08-19 paper/main.tex
Cont. implementing new model.

\subsection{Sample complexity}

\cm{Show that our architecure offers better then generalization than simple, shallow MLP.}
Proof idea: show that GNN can be seen low "degree" (assuming low nnz) compositional functions encoded as a tree, then use results on composiotional function (smaller set of parameters) to derive generalization bounds

>>>>

\subsection{Sample complexity/theoretical justification}

\cm{Show that our architecure offers better then generalization than simple, shallow MLP.}
Proof idea: show that GNN can be seen as low "degree" (assuming low nnz) compositional functions encoded as a tree, then use results on composiotional function (smaller set of parameters) to derive generalization bounds

\cm{Somehow show that architecture of Alg. 2 (MWU) is better than using a standard GNN. Idea: Show that MWU can be recovered to show to always get at ferasible solutions.}
